A state space model for discovering the trajectory dynamics of replay

### 2020-03-12 Article.tex

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure2/Figure2_v3}
\caption{Demonstration of the state space model on real data using both sorted and clusterless spikes on the same SWR. \textbf{(A)} Decoding using sorted spikes (arranged top to bottom). In the top panel, 31 cells on a W-track ordered according to linearized position by their place field peaks. The second panel shows the probability of each dynamic over time as in Figure 1F. Shaded regions correspond to the speed classifications in Figure 1G. The third panel shows the estimated probability of latent position over the course of the SWR as it travels down the center arm toward the right arm. L, R, C correspond to the position of the left, right and center wells respectively. The animal's position is indicated by the red triangle. \textbf{(B)} Decoding using clusterless spikes. The top panel shows multiunit spiking activity from each tetrode. Other panels have the same convention as(A).  \textbf{(C)} 1D MAP estimate of the latent position in (A) projected back into 2D. Color indicates time. The animal's position is denoted by the red circle. Grey lines show the animal's 2D position over the entire epoch. L, R, and C correspond to the left, right and center well as in (A). \textbf{(D)} 1D MAP estimate of the latent position in (B) projected back into 2D. Figure conventions are the same as in (C).
}
\label{Figure2}
\end{figure*}

@@

\section*{Methods}
\subsection*{Experiment and Electrophysiology}
\subsection*{Linearization}
\subsection*{Ripple Detection}
\subsection*{Spike Sorting}
\subsection*{Clusterless Data}
\subsection*{Simulated Data}

>>>>

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure2/Figure2_v3}
\caption{Demonstration of the state space model on real data using both sorted and clusterless spikes on the same SWR. \textbf{(A)} Decoding using sorted spikes (arranged top to bottom). In the top panel, 31 cells on a W-track ordered according to linearized position by their place field peaks. The second panel shows the probability of each dynamic over time as in Figure 1F. Shaded regions correspond to the speed classifications as in Figure 1G. The third panel shows the estimated probability of latent position over the course of the SWR as it travels down the center arm toward the right arm. L, R, C correspond to the position of the left, right and center wells respectively. The animal's position is indicated by the red triangle. \textbf{(B)} Decoding using clusterless spikes. The top panel shows multiunit spiking activity from each tetrode. Other panels have the same convention as(A).  \textbf{(C)} 1D MAP estimate of the latent position in (A) projected back into 2D. Color indicates time. The animal's position is denoted by the red circle. Light grey lines show the animal's 2D position over the entire epoch. L, R, and C correspond to the left, right and center well as in (A). \textbf{(D)} 1D MAP estimate of the latent position in (B) projected back into 2D. Figure conventions are the same as in (C).
}
\label{Figure2}
\end{figure*}

@@

\section*{Methods}
\subsection*{Experiment and Electrophysiology}
\subsection*{Linearization}
\subsection*{Ripple Detection}
Ripple detection performed as in
\subsection*{Spike Sorting}
\subsection*{Clusterless Data}
\subsection*{Simulated Data}
